Continuous Reinforcement Learning

### 2018-06-12 magnitudes.tex
[ADD] Adding macros.
[ADD] Adds...

>>>>

\subsection{Notations}
In what follows, we loosely consider the notion of a $\emph{Markov Decision Process}$
$\mathcal{M}$ with discretization step $\deltat$. Such an MDP is the discretization
of a continuous MDP with discretization step $\deltat$. Notably, this means that
contiguous states are at distance $\bigO{\deltat}$ and that instantaneous rewards
have magnitude $\bigO{\deltat}$ for any policy, i.e.
\begin{align}
	\|s_{t + \deltat} - s_t\| &= \bigO{\deltat}\\
	r_t = \reward_t \deltat, &\quad \reward_t = \bigO{1}.
\end{align}
Policies are functions from the state space $\statespace$ to distributions on the
$\actionspace$
\begin{equation}
	\pi\colon \statespace \mapsto \mathcal{D}\left(\actionspace\right).
\end{equation}
The probability of an action $a$ in a given state $s$ under policy $\pi$ is
denoted by $\pi\left(a\mid s\right)$.

We consider discount factors of the form
\begin{equation}
	\gamma' = \left[1 - (1 - \gamma) \deltat\right],
\end{equation}
so has to have an effective discount factor close to $\gamma$.

The state value function and action-state value function of a policy
$\pi$ are defined as
\begin{align}
	V^\pi(s) &= \BE_\pi\left[
		\sum\limits_{t=s}^\infty
		{\gamma'}^{s - t} \reward_{t + (s-t)\deltat} \deltat
		\mid
		s_t = s
	\right]\\
	Q^\pi(s, a) &= \BE_\pi\left[
		\sum\limits_{t=s}^\infty
		{\gamma'}^{s - t} \reward_s \deltat
		\mid
		s_t = s, a_t = a
	\right].
\end{align}
Both functions satisfy recurrent \emph{Bellman equations}
\begin{align}
	V^\pi(s) &= \BE_\pi\left[
		\reward_t \deltat + \gamma' V^\pi(s_{t + \deltat})
		\mid
	s_t = s\right]\\
	Q^\pi(s, a) &= \BE_\pi\left[
		\reward_t \deltat + \gamma' V^\pi(s_{t + \deltat})
		\mid
	s_t = s, a_t = a\right].
\end{align}

\subsection{$Q^\pi = V^\pi$ in continuous time}
\emph{Q-learning} uses the state-action value function to determine which
action optimizes the future return. However, in continuous time, the state-action
value function no longer carries any information on which action carries the best
return. Intuitively, as the discretization step goes to zero, the difference
in resulting state between two actions is of magnitude $\bigO{\deltat}$. Consequently,
the value functions of the corresponding states, and thus the state-action value functions
only differ by a factor of magnitude $\bigO{\deltat}$.
